% !TEX program = xelatex

\documentclass{resume}
\usepackage{xeCJK}
\setCJKmainfont{Noto Sans CJK TC}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Bing Huan Zhong}

\basicInfo{
  \email{a82611141@gmail.com} \textperiodcentered\ 
  \phone{(+886) 0901379848} \textperiodcentered\ 
  \linkedin[roy4801]{https://www.linkedin.com/in/roy4801}}

%%%%%%%%%%%%%%%%%%%%%%% 教育
\section{\faGraduationCap\ Education}

\datedsubsection{\textbf{Fu Jen Catholic University}, Taipei, Taiwan}{2017 -- 2021}
\textit{B.S.} in  Computer Science of Information Engineering (CS)

%%%%%%%%%%%%%%%%%%%%%%% 經驗
% \section{\faBriefcase\ Experience}

% \datedsubsection{\textbf{FLAG Inc.} California, America}{2012 -- Present}
% \role{Summer Intern}{Manager: xxx}
% Brief introduction: xxx.
% \begin{itemize}
%   \item Implemented xxx feature
%   \item Optimized xxx 5\%
%   \item xxx
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%% 專案
\section{\faTasks\ Projects}

\datedsubsection{\textbf{Rish Engine}}{Apr. 2020 -- Present}
\role{Group Leader}{Group Projects}
{\small https://github.com/rishteam/dod} \\
A minimalistic 2D Game Engine, Using C++, SFML
\begin{itemize}
  \item Entity Component System design
  \item Simple editor allowing developer to make their own scene and able to save in own format
  \item Support scripting language
\end{itemize}

\datedsubsection{\textbf{Course Picker}}{Nov. 2019 -- Dec. 2019}
\role{Group Leader}{Group Projects}
{\small https://github.com/rishteam/db-back} \\
A tool for picking courses in FJU
\begin{itemize}
  \item Browse courses, filter, add/delete favorites, schedule
  \item RESTful API, Android App
\end{itemize}

\datedsubsection{\textbf{RishOJ - Online Judge}}{Apr. 2019 -- Jun. 2019}
\role{Group Leader}{Group Projects}
An online judge system for programming contest, {\small https://github.com/FjuOnlineJudge/oj}
\begin{itemize}
  \item Using Python, flask, MySQL
  \item List, filter programming problems, submit codes, see submissions, ranks, ... etc.
\end{itemize}

\datedsubsection{\textbf{Rifleman}}{Feb. 2019 -- Apr. 2019}
\role{Group Leader}{Group Projects}
A 2D shooter game, {\small https://github.com/william31212/Pygame}
\begin{itemize}
  \item RHFramework {\small https://github.com/roy4801/RHframework}
    \subitem A bare-bone framework for rifleman
  \item Using Python, Pygame, OpenGL, Tiled as map editor
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%% 技能
\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C++ > Python > C 
  \item Scripting Languages: shell script
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%% 獲獎
\section{\faTrophy\ Honors and Awards}

\subsection{Programming Contest}
\datedline{\textit{Gold Place}, ICPC Taiwan NCPU}{Jun. 2020}
\datedline{\textit{Bronze Place}, ICPC Asia Taipei-Hsinchu Regional}{Nov. 2019}
\datedline{\textit{Silver Place}, ICPC Taiwan NCPU}{Jun. 2019}
\datedline{\textit{\nth{2} Place}, USCOJ}{2019}

\subsection{Cybersecurity Contest}
\datedline{\textit{Qualified}, Advanced Information Security Summer School}{2020, 2019, 2018}
\datedline{\textit{\nth{9} /36}, Taiwan Cyber Security Competition}{2020}

%%%%%%%%%%%%%%%%%%%%%%% 社群
\section{\faUsers\ Community}

\subsection{School Club}
\datedline{Director in FJCU NISRA {\small(for Cybersecurity)\ https://www.nisra.net/}}{Jul. 2019 -- Jul. 2020}
\datedline{Lecturer, Member in FJCU NISRA }{Jul. 2017 -- Present}
\datedline{Lecturer, Member in FJCU CPC {\small(for Programming Contest)}}{Jul. 2019 -- Present}
SlideShare: https://www.slideshare.net/ssuserbafcfa

\subsection{Other}
\datedline{General Service Staff, HITCON}{2018}

%%%%%%%%%%%%%%%%%%%%%%% 其他
\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://blog.roy4801.tw
  \item GitHub: https://github.com/roy4801
  \item Languages:
    \subitem 中文 - Native speaker
    \subitem English - TOEIC 895
\end{itemize}

%% Reference
% \newpage
% \bibliographystyle{IEEETran}
% \bibliography{mycite}
\end{document}
